The GWR Smoke's effect on Oregon 2013 Medication of Beta-2 agonists

### 2017-07-27 r_scripts/analysis/oregon_medication.Rmd
Update oregon_medication.Rmd

---
title: "Oregon 2013 Medication for Beta-2 agonists"
author: "Jingyang Liu"
date: "May 17, 2017"
output: html_document
---

```{r library, include=FALSE, echo=FALSE}
library(tidyverse)
# library(data.table)
library(survival)
library(ggplot2)
library(htmlTable)
library(knitr)
library(broom)
library(lme4)
library(maps)
library(lubridate) # date

@@

## Overview

@@

## Method Description

@@

```{r import filtered original data, eval=FALSE, echo=FALSE}
### Import whole data set ------------------------------------------------------
read_path <- paste0("../../../data/data_original/gan_episodes_of_care.txt")
start_time <- Sys.time()
oregon_df <- fread(read_path, sep = "|", showProgress = T) 
stop_time <-  Sys.time() - start_time 
# time it took
stop_time # 7 mins

@@

@@

write_path <- paste0('../../../data/data_new/',
                     'oregon_asthma_sample.csv')
write_csv(or_asthma_sample, write_path)

write_path2 <- paste0('../../../data/data_new/',
                     'oregon_ndc_with_index.csv')

write_csv(or_ndc_asthma_copd_sum, write_path2)

@@

```{r time stratified county for ts, echo=FALSE, include=FALSE, eval=FALSE}
read_path7 <- paste0("../data_new/medication/oregon_asthma_ndc.csv")
or_ndc_claim <- read_csv(read_path7)

@@

@@

print(plot_ts)

@@

print(plot_county)
# print(plot_county_line)
# save figure
ggsave("../plot_new/ndc_county_rate_ts.pdf", plot = plot_county, 
       width = 12, height = 8, units = "in")
ggsave("../plot_new/ndc_county_rate_ts_line.pdf", plot = plot_county_line, 
       width = 12, height = 8, units = "in")

@@

plot(plot_health_smk)
# plot(plot_county_health_smk)

@@

### map of smoke days

```{r smoke days and map, warning=FALSE, message=FALSE, echo=FALSE}
or_ts <- or_ndc_county_ts %>% 
  mutate(smoke0 = ifelse(geo_smk_pm_county > 0, 1, 0),
         smoke5 = ifelse(geo_smk_pm_county > 5, 1, 0),
         smoke10 = ifelse(geo_smk_pm_county > 10, 1, 0),
         smoke15 = ifelse(geo_smk_pm_county > 15, 1, 0), 
         # lag variable
         geo_smk_lag1 = lag(geo_smk_pm10, 1, order_by = county),
         geo_smk_lag2 = lag(geo_smk_pm10, 2, order_by = county),
         geo_smk_lag3 = lag(geo_smk_pm10, 3, order_by = county),
         geo_smk_lag4 = lag(geo_smk_pm10, 4, order_by = county),
         geo_smk_lag5 = lag(geo_smk_pm10, 5, order_by = county),
         geo_smk_lag6 = lag(geo_smk_pm10, 6, order_by = county),
         geo_smk_lag7 = lag(geo_smk_pm10, 7, order_by = county)) %>% 
  ungroup()

@@

smoke_wave <- or_ts %>% 
  select(county, date, geo_wt_pm_county) %>% 
  mutate(high_pm_day = ifelse(geo_wt_pm_county > 16.33, 1, 0)) %>% 
  group_by(county) %>% 
  # identify consecutive days
  mutate(smoke_wave = ifelse(lag(high_pm_day, 
    order_by = county)==1 & high_pm_day ==1, 1, 0)) %>% 
  select(-high_pm_day, -geo_wt_pm_county)

@@

# only 55 smoke wave days
# xtabs(~smoke_wave,  or_ts)
# if we compare to our geo smoke > 10, we'd add 362 extra days
# xtabs(~smoke_wave + smoke10, or_ts)
# if we used smoke >15 we'd add 164 extra days 
# xtabs(~smoke_wave + smoke15, or_ts)

# small multiples dataset
or_smk <- or_ts %>% 
  select(county, date, wrf_smk_pm_county, krig_smk_pm_county, geo_smk_pm_county) %>% 
  gather(key = smk_method, value = pm, -date, -county)

or_smk_plot <- ggplot(or_smk, aes(x = date, y = pm)) +
  geom_point(aes(colour = smk_method), alpha = 0.8, size = 0.8) +
  facet_wrap(~county) +
  ggtitle("Oregon: 2013 Fire Season Smoke PM2.5") +
  ylab("Smoke PM2.5 ug/m^3") +
  xlab("Year 2013") +
  theme_bw()

@@

# data wrangle ----
#first step is to summarise the counts of smoke days in each county 
or_smk_count <- or_ts %>% 
  group_by(county) %>% 
  # summing up smoke days
  summarise(smk_wave_n = sum(smoke_wave), smk_day0 = sum(smoke0), 
            smk_day5 = sum(smoke5), smk_day10 = sum(smoke10),
            smk_day15 = sum(smoke15)) %>% 
  # county needs to be lowercase to join to maps dataframe
  mutate(county = tolower(county))

@@

# join county counts to map df
or_smk_df <- or_county_df %>% 
  right_join(or_smk_count, by = c("subregion" = "county")) %>% 
  # small multiples of different smoke cutoff methods
  gather(key = smk_cut_method, value = smoke_days, -long:-subregion) %>% 
  # filter out smoke day 0 since it's not very specific
  filter(smk_cut_method != "smk_day0") %>% 
  # rename smoke day cutoffs 
  mutate(smk_cut_method = 
    ifelse(smk_cut_method == "smk_day5","Smoke PM2.5 > 5 ug/m^3",
    ifelse(smk_cut_method == "smk_day10", "Smoke PM2.5 > 10 ug/m^3",
    ifelse(smk_cut_method == "smk_day15", "Smoke PM2.5 > 15 ug/m^3",
    ifelse(smk_cut_method == "smk_wave_n", "Smoke Wave", NA)))),
    # preserve smoke method order for small multiple
    smk_cut_method = factor(smk_cut_method, 
      levels = c("Smoke PM2.5 > 5 ug/m^3", "Smoke PM2.5 > 10 ug/m^3", 
                 "Smoke PM2.5 > 15 ug/m^3", "Smoke Wave")))

@@

# smoke days where GWR smoke > 15
smoke_map <- ggplot(or_smk_df, aes(x=long, y=lat, group=group)) +
  # fill with number of smoke days
  geom_polygon(aes(fill = smoke_days), alpha = 0.7) +
  scale_fill_gradient("Smoke-Impacted Days",
                      low = "#0b486b", high = "#f56217") +
  # add county path on top
  geom_path() +
  facet_wrap(~smk_cut_method) +
  xlab("Longitude") +
  ylab("Latitude") +
  ggtitle("Oregon: Counties affected by smoke") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA))

smoke_map

@@

@@

## ggplot 
  print_plot <- ggplot(wrf_geo_age_plot,
    aes(x = pm_method, y = odds_ratio, color = pm_method), na.rm = T) +
    geom_point(position = position_dodge(width = 0.5), na.rm = T) + 
    geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                  position = position_dodge(width = 0.5), width = 0.2, na.rm =T) +
    # custom color 
    scale_color_manual(name = "Smoke-Estimation Method", 
                       values = c("red",  "blue", "#32115C"),
                       guide = guide_legend(title.position = "top", title.hjust = 0.5)) +
    facet_wrap(~outcome, nrow = 3, scales = "free") +
    geom_hline(yintercept = 1, linetype=2) +
    #ggtitle('Association Between PM2.5 from \n Wildfire Smoke on Hospitalizations') +
    ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in PM"[2.5]))) +
    #ylim(0, 2) +
    xlab('Overall') +
    # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element
    #axis.text.x = element_blank(),
    #axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90),
    # legend elements
    legend.position = "bottom")
    #legend.text = element_text(size = 8))

@@

### Time-Stratified by Age Categories

## ggplot 
  print_plot <- ggplot(wrf_geo_age_plot,
    aes(x = age_cat2, y = odds_ratio, color = pm_method), na.rm = T) +
    geom_point(position = position_dodge(width = 0.5), na.rm = T) + 
    geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                  position = position_dodge(width = 0.5), width = 0.2, na.rm =T) +
    # custom color 
    scale_color_manual(name = "Smoke-Estimation Method", 
                       values = c("red",  "blue", "#32115C"),
                       guide = guide_legend(title.position = "top", title.hjust = 0.5)) +
    facet_wrap(~outcome, nrow = 3, scales = "free") +
    geom_hline(yintercept = 1, linetype=2) +
    #ggtitle('Association Between PM2.5 from \n Wildfire Smoke on Hospitalizations') +
    ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in PM"[2.5]))) +
    #ylim(0, 2) +
    xlab('Age Category ') +
    # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10), 
    # axis element
    #axis.text.x = element_blank(),
    #axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90),
    # legend elements
    legend.position = "bottom")
    #legend.text = element_text(size = 8))

## ggplot
  print_plot <- ggplot(wrf_geo_sex_plot,
    aes(x = sex_cat, y = odds_ratio, color = pm_method), na.rm = T) +
    geom_point(position = position_dodge(width = 0.5), na.rm = T) + 
    geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                  position = position_dodge(width = 0.5), width = 0.2, na.rm =T) +
    # custom color 
    scale_color_manual(name = "Smoke-Estimation Method", 
                       values = c("red", "blue", "#32115C"),
                       guide = guide_legend(title.position = "top", title.hjust = 0.5)) +
    facet_wrap(~outcome, nrow = 3, scales = "free") +
    geom_hline(yintercept = 1, linetype=2) +
    #ggtitle('Association Between PM2.5 from \n Wildfire Smoke on Hospitalizations') +
    ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in PM"[2.5]))) +
    #ylim(0, 2) +
    xlab('Sex') +
    # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element
    #axis.text.x = element_blank(),
    #axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90),
    # legend elements
    legend.position = "bottom")
    #legend.text = element_text(size = 8))

@@

## Supplement
### 1. For Overall Plot (Unconstrained lag model)

```{r overall lags, warning =F, echo = F, results='asis'} 
# dataframe list
method_list <- c('Geo-Weighted Smoke')

@@

## ggplot 
  print_plot <- ggplot(wrf_geo_lag_plot,
    aes(x = lag, y = odds_ratio, color = lag), na.rm = T) +
    geom_point(position = position_dodge(width = 0.5), na.rm = T) + 
    geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                  position = position_dodge(width = 0.5), width = 0.2, na.rm =T) +
    # custom color 
    scale_color_manual(name = "Geo-smk Lag", 
                       values = rep(c("black"), 7),
                       guide = guide_legend(title.position = "top", title.hjust = 0.5)) +
    facet_wrap(~outcome, nrow = 7, scales = "free") +
    geom_hline(yintercept = 1, linetype=2) +
    #ggtitle('Association Between PM2.5 from \n Wildfire Smoke on Hospitalizations') +
    ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in PM"[2.5]))) +
    #ylim(0, 2) +
    xlab('Smoke Estimation Method') +
    # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element
    #axis.text.x = element_blank(),
    #axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90),
    # legend elements
    legend.position = "bottom")
    #legend.text = element_text(size = 8))

@@

```{r unconstrained ts lag, message=FALSE, echo=FALSE, warning=FALSE}
or_ndc_county_ts_df <- or_ndc_county_ts %>%
  select(1:4, pop, rate_per_100k, day, geo_smk_pm_county,
         geo_smk_pm_lag1_county:geo_smk_pm_lag7_county, wrf_temp_county,
         wrf_temp_lag1_county:wrf_temp_lag7_county) %>%
  mutate(geo_smk_pm10_county = geo_smk_pm_county/10,
         geo_smk_pm10_lag1_county =geo_smk_pm_lag1_county/10,
         geo_smk_pm10_lag2_county =geo_smk_pm_lag2_county/10,
         geo_smk_pm10_lag3_county =geo_smk_pm_lag3_county/10,
         geo_smk_pm10_lag4_county =geo_smk_pm_lag4_county/10,
         geo_smk_pm10_lag5_county =geo_smk_pm_lag5_county/10,
         geo_smk_pm10_lag6_county =geo_smk_pm_lag6_county/10,
         geo_smk_pm10_lag7_county =geo_smk_pm_lag7_county/10) 
  # filter(!is.na(geo_smk_pm10_lag7_zip))

@@

plot_rr <- ggplot(rr_df, aes(x=lag, y = rel_risk)) +
  geom_point() +
  geom_errorbar(aes(ymin=lower_95, ymax=upper_95), width = 0.2) +
  geom_hline(yintercept = 1, linetype = 2, colour = "red") +
  theme(
   panel.background = element_rect(fill = 'white', colour = 'black'),
   panel.grid.major = element_blank(),
   panel.grid.minor = element_blank(),
   axis.text.x = element_text(angle = 90, vjust = .75)) +
  ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in PM"[2.5]))) +
  xlab("Outcome") +
  ggtitle("Relative Risk for a 10ug/m^3 increase PM2.5 estimated via GWR Smoke")

>>>>

---
title: "The GWR Smoke's effect on Oregon 2013 Medication of Beta-2 agonists"
author: "Jingyang Liu"
date: "May 17, 2017"
output: html_document
---

```{r library, include=FALSE, echo=FALSE}
library(tidyverse)
# library(data.table)
library(survival)
library(ggplot2)
library(htmlTable)
library(knitr)
library(broom)
library(lme4)
library(maps)
library(lubridate) # date
library(ggrepel)
library(sp)

@@

# server
library(dplyr)
library(data.table)
library(readxl) 
library(readr)

## Overview (1, 2)

1. Intro: We found an association with wildfire smoke and respiratory outcomes in Washington state 2012 using a novel estimate of smoke concentration, geo-graphically weighted ridge regression (GWR). We want to know if smoke impacts other health outcomes, specifically respiratory rescue medications (beta 2 agonists) (abbreviate to SABA)

2. Research question: We evaluated the association between smoke concentrations using the GWR method and SABA refills in Oregon state during the 2013 wildfire season.

@@

## Method Description (3)

3.Methods: use case-crossover for all health outcome figures and results. Make sure smoke is assigned via zipcode. For the descriptive of smoke, I think the county-level for now. We may move to zip.

@@

```{r import filtered original data and make index, eval=FALSE, echo=FALSE}
### Import whole data set ------------------------------------------------------
read_path <- paste0("../../../data/data_original/gan_episodes_of_care.txt")
start_time <- Sys.time()
oregon_df <- fread(read_path, sep = "|", showProgress = T) 
stop_time <-  Sys.time() - start_time 
# time it took
stop_time # 7 mins

@@

write_path4 <- paste0('../../../data/data_new/',
                     'oregon_beta_ndc_index_full.csv')
write_csv(oregon_ndc_index, write_path4)

@@

# write_path <- paste0('../../../data/data_new/',
#                      'oregon_asthma_sample.csv')
# write_csv(or_asthma_sample, write_path)

# write_path2 <- paste0('../../../data/data_new/',
#                      'oregon_ndc_with_index.csv')

# write_csv(or_ndc_asthma_copd_sum, write_path2)

@@

```{r time stratified county for ndc ts, echo=FALSE, include=FALSE, eval=FALSE}
read_path7 <- paste0("../data_new/medication/oregon_asthma_ndc.csv")
or_ndc_claim <- read_csv(read_path7)

@@

```{r time stratified county smk for ts, echo=FALSE, include=FALSE, eval=FALSE}
read_path_county_pm <- paste0("../data_new/county_data/or_county_pop_wt_pm.csv")
county_smoke <- read_csv(read_path_county_pm) # 5508 rows

or_county_ts <- county_smoke_w_lag %>%
  mutate(day = ifelse(weekdays(date) == "Monday" |
                      weekdays(date) == "Tuesday" |
                      weekdays(date) == "Wednesday"|
                      weekdays(date) == "Thursday"|
                      weekdays(date) == "Friday", "weekday",
               ifelse(weekdays(date) == "Saturday" |
                      weekdays(date) == "Sunday", "weekend", NA))) %>%
  group_by(county, date) %>%
  mutate(geo_smk_pm10 = geo_smk_pm_county/10)

or_county_ts$day[which(or_county_ts$date=="2013-05-27")] <- "weekend"
or_county_ts$day[which(or_county_ts$date=="2013-07-04")] <- "weekend"
or_county_ts$day[which(or_county_ts$date=="2013-09-02")] <- "weekend"

write_path5 <- paste0("../data_new/medication/or_county_time_series.csv")
write_csv(or_county_ts, write_path5)

@@

# print(plot_ts)

@@

# print(plot_county)
# print(plot_county_line)
# save figure
ggsave("../plot_new/ndc_county_rate_ts.pdf", plot = plot_county, 
       width = 12, height = 8, units = "in")
ggsave("../plot_new/ndc_county_rate_ts_line.pdf", plot = plot_county_line, 
       width = 12, height = 8, units = "in")

@@

# plot(plot_health_smk)
# plot(plot_county_health_smk)

@@

### map of smoke days (4)

```{r smoke days and map, warning=FALSE, message=FALSE, echo=FALSE}
read_path6 <- paste0("../data_new/medication/or_county_time_series.csv")
or_county_ts <- read_csv(read_path6)

or_ts <- or_county_ts %>% 
  mutate(smoke0 = ifelse(geo_smk_pm_county > 0, 1, 0),
         smoke5 = ifelse(geo_smk_pm_county > 5, 1, 0),
         smoke10 = ifelse(geo_smk_pm_county > 10, 1, 0),
         smoke15 = ifelse(geo_smk_pm_county > 15, 1, 0), 
         # lag variable
         geo_smk_lag1 = lag(geo_smk_pm10, 1, order_by = county),
         geo_smk_lag2 = lag(geo_smk_pm10, 2, order_by = county),
         geo_smk_lag3 = lag(geo_smk_pm10, 3, order_by = county),
         geo_smk_lag4 = lag(geo_smk_pm10, 4, order_by = county),
         geo_smk_lag5 = lag(geo_smk_pm10, 5, order_by = county),
         geo_smk_lag6 = lag(geo_smk_pm10, 6, order_by = county),
         geo_smk_lag7 = lag(geo_smk_pm10, 7, order_by = county)) %>% 
  ungroup()

@@

smoke_wave <- or_ts %>% 
  select(county, date, geo_wt_pm_county) %>% 
  mutate(high_pm_day = ifelse(geo_wt_pm_county > 10, 1, 0)) %>% 
  group_by(county) %>% 
  # identify consecutive days
  mutate(smoke_wave = ifelse(lag(high_pm_day, 
    order_by = county)==1 & high_pm_day ==1, 1, 0)) %>% 
  select(-high_pm_day, -geo_wt_pm_county)

@@

# small multiples dataset
or_smk <- or_ts %>% 
  select(county, date, geo_smk_pm_county) %>% 
  gather(key = smk_method, value = pm, -date, -county)

or_smk_plot <- ggplot(or_smk, aes(x = date, y = pm)) +
  geom_point(aes(colour = smk_method), alpha = 0.8, size = 0.8) +
  facet_wrap(~county) +
  ggtitle(expression("Oregon: 2013 Fire Season Smoke PM"[2.5])) +
   theme(legend.position="none") +
   # theme(axis.text.x=element_blank()) +
  theme(panel.background = element_rect(fill = 'white', colour = 'white')) +
  theme(strip.background = element_rect(colour = "white", fill = "white"))+
  ylab(expression(paste("GWR Smoke PM"[2.5], " Concentration, µg/m^3" ))) +
  xlab("May 1st to Sep 30th in 2013") +
  theme(axis.line.x = element_line(color="black"),
        axis.line.y = element_line(color="black"))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

 # data wrangle ----
#first step is to summarise the counts of smoke days in each county 
or_smk_count <- or_ts %>% 
  group_by(county) %>% 
  # summing up smoke days
  summarise(smk_day10 = sum(smoke10)) %>% 
  # county needs to be lowercase to join to maps dataframe
  mutate(county = tolower(county))

@@

# join county counts to map df
or_smk_df <- or_county_df %>% 
  right_join(or_smk_count, by = c("subregion" = "county")) %>% 
  # small multiples of different smoke cutoff methods
  gather(key = smk_cut_method, value = smoke_days, -long:-subregion) %>% 
  # filter out smoke day 0 since it's not very specific
  filter(smk_cut_method != "smk_day0") %>% 
  # rename smoke day cutoffs 
  mutate(smk_cut_method = 
    ifelse(smk_cut_method == "smk_day10", "Smoke PM2.5 > 10 ug/m^3", NA),
    # preserve smoke method order for small multiple
    smk_cut_method = factor(smk_cut_method, 
      levels = c("Smoke PM2.5 > 10 ug/m^3")))

@@

# or_county <- or_smk_df %>%
#   group_by(subregion) %>%
#   summarise(ave_long = mean(long), ave_lat = mean(lat))

# or_county$subregion <- gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", or_county$subregion, perl=TRUE)

getLabelPoint <- # Returns a county-named list of label points
  function(county) {Polygon(county[c('long', 'lat')])@labpt}

centroids <- by(or_smk_df, or_smk_df$subregion, getLabelPoint)     # Returns list
centroids <- do.call("rbind.data.frame", centroids)  # Convert to Data Frame
names(centroids) <- c('long', 'lat')                 # Appropriate Header

rownames(centroids) <- gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", rownames(centroids), perl=TRUE)

# smoke days where GWR smoke > 15
smoke_map <- ggplot(or_smk_df, aes(x=long, y=lat, group=group)) +
  # fill with number of smoke days
  geom_polygon(aes(fill = smoke_days), alpha = 0.7) +
  scale_fill_gradient("Smoke-Impacted Days",
                      low = "#3964C3", high = "#dc2430") +
  # add county path on top
  geom_path() +
  facet_wrap(~smk_cut_method) +
   theme(strip.background = element_blank(),
       strip.text.x = element_blank()) +
  xlab("Longitude") +
  ylab("Latitude") +
  ggtitle("Oregon: Counties Affected by Smoke PM2.5 > 10µg/m^3") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA)) +
  geom_text_repel(data = centroids, aes(long, lat, label = rownames(centroids), group=NULL), size = 2.5)

smoke_map1 <- ggplot(or_smk_df, aes(x=long, y=lat, group=group)) +
  # fill with number of smoke days
  geom_polygon(aes(fill = smoke_days), alpha = 0.7) +
  scale_fill_gradient("Smoke-Impacted Days",
                      low = "#3964C3", high = "#dc2430") +
  # add county path on top
  geom_path() +
  facet_wrap(~smk_cut_method) +
   theme(strip.background = element_blank(),
       strip.text.x = element_blank()) +
  xlab("Longitude") +
  ylab("Latitude") +
  ggtitle("Oregon: Counties Affected by Smoke PM2.5 > 10µg/m^3") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA)) +
  geom_text(data = centroids, aes(long, lat, label = rownames(centroids), group=NULL), size = 2)
smoke_map

smoke_map1

@@

### Outcomes

```{r category, echo = F, message = F, warning = F, results='asis', eval=FALSE}
read_path <- paste0("../data_new/medication/oregon_beta_ndc_index_full.csv")
inhaler_ndc <- read_csv(read_path)

@@

## ggplot 
  print_plot <- ggplot(wrf_geo_age_plot,
    aes(x = pm_method, y = odds_ratio, color = pm_method), na.rm = T) +
    geom_point(position = position_dodge(width = 0.5), na.rm = T) + 
    geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                  position = position_dodge(width = 0.5), width = 0.2, na.rm =T) +
    # custom color 
    scale_color_manual(name = "Smoke-Estimation Method", 
                       values = c("red",  "blue", "#32115C"),
                       guide = guide_legend(title.position = "top", title.hjust = 0.5)) +
    facet_wrap(~outcome, nrow = 3, scales = "free") +
    geom_hline(yintercept = 1, linetype=2) +
    #ggtitle('Association Between PM2.5 from \n Wildfire Smoke on Hospitalizations') +
    ylab(expression(paste("Odds Ratio for 10Âµg/m"^3, " Increase in PM"[2.5]))) +
    #ylim(0, 2) +
    xlab('Overall') +
    # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element
    #axis.text.x = element_blank(),
    #axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90),
    # legend elements
    legend.position = "bottom")
    #legend.text = element_text(size = 8))

@@

@@

## Supplement

### Age and Sex category (8)
### Time-Stratified by Age Categories

## ggplot 
  print_plot <- ggplot(wrf_geo_age_plot,
    aes(x = age_cat2, y = odds_ratio, color = pm_method), na.rm = T) +
    geom_point(position = position_dodge(width = 0.5), na.rm = T) + 
    geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                  position = position_dodge(width = 0.5), width = 0.2, na.rm =T) +
    # custom color 
    scale_color_manual(name = "Smoke-Estimation Method", 
                       values = c("red",  "blue", "#32115C"),
                       guide = guide_legend(title.position = "top", title.hjust = 0.5)) +
    facet_wrap(~outcome, nrow = 3, scales = "free") +
    geom_hline(yintercept = 1, linetype=2) +
    #ggtitle('Association Between PM2.5 from \n Wildfire Smoke on Hospitalizations') +
    ylab(expression(paste("Odds Ratio for 10Âµg/m"^3, " Increase in PM"[2.5]))) +
    #ylim(0, 2) +
    xlab('Age Category ') +
    # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10), 
    # axis element
    #axis.text.x = element_blank(),
    #axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90),
    # legend elements
    legend.position = "bottom")
    #legend.text = element_text(size = 8))

## ggplot
  print_plot <- ggplot(wrf_geo_sex_plot,
    aes(x = sex_cat, y = odds_ratio, color = pm_method), na.rm = T) +
    geom_point(position = position_dodge(width = 0.5), na.rm = T) + 
    geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                  position = position_dodge(width = 0.5), width = 0.2, na.rm =T) +
    # custom color 
    scale_color_manual(name = "Smoke-Estimation Method", 
                       values = c("red", "blue", "#32115C"),
                       guide = guide_legend(title.position = "top", title.hjust = 0.5)) +
    facet_wrap(~outcome, nrow = 3, scales = "free") +
    geom_hline(yintercept = 1, linetype=2) +
    #ggtitle('Association Between PM2.5 from \n Wildfire Smoke on Hospitalizations') +
    ylab(expression(paste("Odds Ratio for 10Âµg/m"^3, " Increase in PM"[2.5]))) +
    #ylim(0, 2) +
    xlab('Sex') +
    # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element
    #axis.text.x = element_blank(),
    #axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90),
    # legend elements
    legend.position = "bottom")
    #legend.text = element_text(size = 8))

### 1. For Overall Plot (Unconstrained lag model)

```{r overall lags, warning =F, echo = F, results='asis', eval=FALSE} 
# dataframe list
method_list <- c('Geo-Weighted Smoke')

@@

## ggplot 
  print_plot <- ggplot(wrf_geo_lag_plot,
    aes(x = lag, y = odds_ratio, color = lag), na.rm = T) +
    geom_point(position = position_dodge(width = 0.5), na.rm = T) + 
    geom_errorbar(aes(ymin=lower95, ymax=upper95), 
                  position = position_dodge(width = 0.5), width = 0.2, na.rm =T) +
    # custom color 
    scale_color_manual(name = "Geo-smk Lag", 
                       values = rep(c("black"), 7),
                       guide = guide_legend(title.position = "top", title.hjust = 0.5)) +
    facet_wrap(~outcome, nrow = 7, scales = "free") +
    geom_hline(yintercept = 1, linetype=2) +
    #ggtitle('Association Between PM2.5 from \n Wildfire Smoke on Hospitalizations') +
    ylab(expression(paste("Odds Ratio for 10Âµg/m"^3, " Increase in PM"[2.5]))) +
    #ylim(0, 2) +
    xlab('Smoke Estimation Method') +
    # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element
    #axis.text.x = element_blank(),
    #axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90),
    # legend elements
    legend.position = "bottom")
    #legend.text = element_text(size = 8))

@@

```{r unconstrained ts lag, message=FALSE, echo=FALSE, warning=FALSE, eval=FALSE}
or_ndc_county_ts_df <- or_ndc_county_ts %>%
  select(1:4, pop, rate_per_100k, day, geo_smk_pm_county,
         geo_smk_pm_lag1_county:geo_smk_pm_lag7_county, wrf_temp_county,
         wrf_temp_lag1_county:wrf_temp_lag7_county) %>%
  mutate(geo_smk_pm10_county = geo_smk_pm_county/10,
         geo_smk_pm10_lag1_county =geo_smk_pm_lag1_county/10,
         geo_smk_pm10_lag2_county =geo_smk_pm_lag2_county/10,
         geo_smk_pm10_lag3_county =geo_smk_pm_lag3_county/10,
         geo_smk_pm10_lag4_county =geo_smk_pm_lag4_county/10,
         geo_smk_pm10_lag5_county =geo_smk_pm_lag5_county/10,
         geo_smk_pm10_lag6_county =geo_smk_pm_lag6_county/10,
         geo_smk_pm10_lag7_county =geo_smk_pm_lag7_county/10) 
  # filter(!is.na(geo_smk_pm10_lag7_zip))

@@

plot_rr <- ggplot(rr_df, aes(x=lag, y = rel_risk)) +
  geom_point() +
  geom_errorbar(aes(ymin=lower_95, ymax=upper_95), width = 0.2) +
  geom_hline(yintercept = 1, linetype = 2, colour = "red") +
  theme(
   panel.background = element_rect(fill = 'white', colour = 'black'),
   panel.grid.major = element_blank(),
   panel.grid.minor = element_blank(),
   axis.text.x = element_text(angle = 90, vjust = .75)) +
  ylab(expression(paste("Odds Ratio for 10Âµg/m"^3, " Increase in PM"[2.5]))) +
  xlab("Outcome") +
  ggtitle("Relative Risk for a 10ug/m^3 increase PM2.5 estimated via GWR Smoke")
